---
title: "Ancestry Product Analytics Homework Assignment"
author: "Trenton Pulsipher"
date: "11/10/2018"
output: html_document
---


```{r settings, echo = F, warning = F, message = F, error = F}
knitr::opts_chunk$set(
  echo = F,
  message = F,
  warning = F,
  error = F,
  fig.height = 3,
  fig.width = 9.5,
  cache = F
)

# Libraries 
library(lubridate)
library(stopwords)
library(tidyverse)
library(trelliscopejs)
library(wordcloud)
library(HSPSUtils) # install_github("HSPS-DataScience/HSPSUtils")
                   # devtools::update_packages("HSPSUtils")
library(rbokeh)
library(ggpubr)
```


```{r dataIn}
# Read in Data
data <- read_csv("~/Documents/Development/R/data/ancestryTest/take-home_exercise_data.csv") %>%
  select(-X1) %>%
  rename(customer_type_grp = customer_type_group)
```


## Initial Look at Data

### Dataset 

```{r dataTable}
create_datetable <- function(data) {
  ## data table
  DT::datatable(
    data, # %>%
      # sample_n(1000),
      options = list(
        pageLength = 5,
        searching = T,
        scrollX = T
      )
    )
}
create_datetable(data)
```


### Data Summary

```{r dataSummary}
create_data_summary <- function(data) {
  # convert column names for use here
  names(data) <- str_replace_all(names(data), "_", ".")

  # Data Summary
  data_summary <- data %>%
    # select_if(is.numeric) %>%
    summarise_all(funs(
      numUnique = length(unique(.)),
      nas = sum(is.na(.)),
      max = max(., na.rm = T),
      min = min(., na.rm = T),
      mean = mean(., na.rm = T))) %>%
    gather() %>%
    separate(key, c("key", "stat"), sep = "_") %>%
    spread(key, value)
  # generate datatable from summary
  DT::datatable(
    data_summary,
    options = list(
      pageLength = 5,
      searching = T,
      scrollX = T
    )
  )
}
create_data_summary(data)
```


### Categorical Variables in Bar Charts

```{r catBarCharts, fig.height = 6}
create_bar_chart_categorical_trelli <- function(data) {
    data %>%
    # selection of categorical variables isn't automated yet
      select(xsell_gsa, regtenure, customer_type_grp, daystogetresult_grp, 
             dna_visittrafficsubtype) %>%
      gather_group_by_count() %>%
      ungroup() %>%
    ggplot(aes(x = value, y = Count)) +
      geom_bar(stat = "identity", alpha = 0.5) +
      geom_text(aes(label = scales::comma(Count))) +
      theme_bw() +
      coord_flip() +
      labs(x = "", y = "") +
      facet_wrap(~key, scales = "free")
      # facet_trelliscope(~ key,
      #                   scales = "free",
      #                   self_contained = T,
      #                   width = 600,
      #                   name = "categoricalVariables",
      #                   group = "vars",
      #                   desc = "All Variables of Type Character or Factor")
}
create_bar_chart_categorical_trelli(data)
```


### Numeric Variables in Histograms

```{r numHistograms}
create_hist_numeric <- function(data) {
  ## histogram of all numeric variables
  data %>%
    select(xsell_day_exact) %>%
    # select_if(is.numeric) %>%
    # .select_non_id_columns() %>%
    gather() %>%
    filter(value >= 0) %>%
  ggplot(aes(x = value)) +
    geom_histogram(binwidth = .25, bins = 30) +
    scale_y_continuous(labels = scales::comma) +
    scale_x_log10(breaks = c(0.1, 1, 10, 100, 1000, 10000),
                  labels = c(0.1, 1, 10, 100, 1000, 10000)) +
    facet_wrap(~ key, scales = "free", ncol = 3) +
    theme_bw()
}
create_hist_numeric(data)
```


### Time Series Variables

```{r ts1, fig.height = 4}
create_time_series <- function(data) {
  # time series
  data %>%
    select_if(is.Date) %>%
    gather_group_by_count() %>%
    ungroup() %>%
    figure(xlab = "") %>%
      ly_points(x = value, y = Count,
               hover = list(
                 Date = value, Count = Count
               ))
  # ggplot(aes(x = value, y = Count)) +
  #   geom_line() +
  #   geom_smooth(method = "loess") +
  #   theme_bw() +
  #   facet_wrap(~ key, scales = "free") + 
  #   labs(x = "")
}
create_time_series(data %>% select(ordercreatedate))
```

```{r ts2, fig.height = 4}
create_time_series(data %>% select(dnatestactivationdayid))
```


## Outliers and Notes

* ID variables
    + ```r data %>% group_by(prospectid) %>% mutate(Count = n()) %>% filter(Count > 1) %>% pull(prospectid) %>% unique() %>% length() %>% scales::comma()``` **prospectid**s appear multiple times, accounting for ```r data %>% group_by(prospectid) %>% mutate(Count = n()) %>% filter(Count > 1) %>% pull(prospectid) %>% length() %>% scales::comma()``` rows in the dataset
* Categorical variables
    + **dna_visittrafficsubtype** has roughly 15 non-NA subtypes over 2000, meaning many subtypes contain very few (for some it's almost no) observations in this dataset
    + Treating **xsell_gsa** as categorical.
* Numeric variables
    + **xsell_day_exact** appears to have a funky distribution, quite log looking. However, the histogram does ignore any zero values, which is roughly ```r round((data %>% select(xsell_day_exact) %>% filter(xsell_day_exact == 0) %>% count()) / ((data %>% select(xsell_day_exact) %>% filter(xsell_day_exact == 0) %>% count()) + (data %>% select(xsell_day_exact) %>% filter(xsell_day_exact != 0) %>% count())), 3) * 100```% of the values for that variable. May want to look at a cummulative view of some kind.
* Time series variables
    + **ordercreatedate** has a date of `r data %>% select(ordercreatedate) %>% filter(ordercreatedate < "2000-01-01") %>% slice(1) %>% pull()` repeated `r data %>% select(ordercreatedate) %>% filter(ordercreatedate < "2000-01-01") %>% count() %>% pull()` times in the dataset. (Suggest removing these from the dataset.)
    + **dnatestactivationdayid** has `r round((data %>% select(dnatestactivationdayid) %>% filter(is.na(dnatestactivationdayid)) %>% count()) / (data %>% select(dnatestactivationdayid) %>% count()), 3) * 100 `% of the values as NA.


### Categorial Variable Notes

A closer look at dna_visittrafficsubtype shows that many of the subtypes are rarely found in this dataset.
```{r tblVisitTraffic}
knitr::kable(data %>% 
        group_by(dna_visittrafficsubtype) %>% 
        summarise(Count = n()) %>% 
        mutate(
          
          Percent = 100 * (Count / sum(Count))
        ) %>% 
        arrange(desc(Percent)),
     format = "markdown",
     padding = 2) 
```


### Time Series Variables (improved)

After removing the outlier dates (noted above) for ordercreatedate we can better see the general trend.
```{r tsImproved1, fig.height = 4}
create_time_series(data %>% 
                     filter(
                       ordercreatedate > "2000-01-01",
                       !is.na(dnatestactivationdayid)
                     ) %>%
                     select(ordercreatedate)
                   )
```

After removing the NAs from dnatestactivationdayid we can better see the general trend.
```{r tsImproved2, fig.height = 4}
create_time_series(data %>% 
                     filter(
                       ordercreatedate > "2000-01-01",
                       !is.na(dnatestactivationdayid)
                     ) %>%
                     select(dnatestactivationdayid)
                   )
```
